\documentclass[11pt, a4paper]{article}
\usepackage{cmap}                        % Поддержка поиска русских слов в PDF (pdflatex)
\usepackage[T2A]{fontenc}                        % Внутренняя кодировка LaTeX
\usepackage[cp1251]{inputenc}            % Выбор языка и кодировки
\usepackage[russian]{babel}
\usepackage{amsmath,amssymb,amsthm}
% Геометрия страницы
\usepackage[margin=20mm]{geometry}
\usepackage[unicode, pdfborder={0 0 0}]{hyperref}

%\binoppenalty=1000000
%\relpenalty=1000000
\pretolerance=400
\tolerance=1500

\begin{document}

\thispagestyle{empty}
\renewcommand{\refname}{Публикации, цитирующие работы А.Н. Максименко}
\begin{thebibliography}{12}
\bibitem{Pilaud:2010} Pilaud V. (2010). Multitriangulations, pseudotriangulations and some problems of realization of polytopes. PhD thesis. Universite Paris Diderot. \url{https://arxiv.org/pdf/1009.1605.pdf}
\begin{itemize}
\item The diameter of the ridge-graph of a cyclic polytope.
\end{itemize}
\bibitem{Beasley:2013} Beasley, L. B., Klauck, H., Lee, T., Theis, D. O. (2013). Communication complexity, linear optimization, and lower bounds for the nonnegative rank of matrices (Dagstuhl Seminar 13082). In Dagstuhl Reports (Vol. 3, No. 2). Schloss Dagstuhl-Leibniz-Zentrum fuer Informatik. \url{http://drops.dagstuhl.de/opus/volltexte/2013/4019/pdf/dagrep_v003_i002_p127_s13082.pdf}
\begin{itemize}
	\item An analog of the Cook theorem for polytopes.
\end{itemize}
\bibitem{Fiorini:2014} Fiorini, S., Massar, S., Patra, M. K., Tiwary, H. R. (2014). Generalized probabilistic theories and conic extensions of polytopes. Journal of Physics A: Mathematical and Theoretical, 48(2), 025302. \url{http://iopscience.iop.org/article/10.1088/1751-8113/48/2/025302/meta}
\begin{itemize}
	\item An analog of the Cook theorem for polytopes.
\end{itemize}
\bibitem{Qi:2015} Qi, K., Feng, Q., Zhao, K. (2015). A disruption model based emergent reconfiguration method for aircraft fleet support station failure. In Reliability Systems Engineering (ICRSE), 2015 First International Conference on (pp. 1--6). IEEE.
\url{http://ieeexplore.ieee.org/abstract/document/7366520/}
\begin{itemize}
	\item The simplest families of polytopes associated with NP-hard problems
\end{itemize}
\bibitem{Huq:2016} Huq A. The Complexity of Extended Formulations (2016). PhD Thesis. Georgia Institute of Technology.
\url{https://smartech.gatech.edu/handle/1853/55556}
\begin{itemize}
	\item An analog of the Cook theorem for polytopes.
\end{itemize}
\bibitem{Fawzi:2016} Fawzi, H., Saunderson, J., Parrilo, P. A. (2016). Sparse sums of squares on finite abelian groups and improved semidefinite lifts. Mathematical Programming, 160(1--2), 149--191. \url{https://link.springer.com/article/10.1007/s10107-015-0977-z}
\begin{itemize}
	\item Small extended formulations for cyclic polytopes.
\end{itemize}
\bibitem{Fawzi:PhD} Fawzi H. (2016). Power and limitations of convex formulations via linear and semidefinite programming lifts. PhD Thesis. Massachusetts Institute of Technology.
\url{http://www.damtp.cam.ac.uk/user/hf323/Fawzi_PhDthesis.pdf}
\begin{itemize}
	\item Small extended formulations for cyclic polytopes.
\end{itemize}
\bibitem{Makkeh:2017} Makkeh, A., Pourmoradnasseri, M., Theis, D. O. (2017). The Graph of the Pedigree Polytope is Asymptotically Almost Complete. In Conference on Algorithms and Discrete Applied Mathematics (pp. 294--307). Springer, Cham.
\url{https://link.springer.com/chapter/10.1007/978-3-319-53007-9_26}
\begin{itemize}
	\item The common face of some 0/1-polytopes with NP-complete non-adjacency relation.
\end{itemize}
\bibitem{Pourmoradnasseri:PhD} Pourmoradnasseri M. (2017). Some Problems Related to Extensions of Polytopes. PhD Thesis. University of Tartu. \url{https://dspace.ut.ee/bitstream/handle/10062/56293/pourmoradnasseri_mozhgan.pdf?sequence=5}
\begin{itemize}
	\item The common face of some 0/1-polytopes with NP-complete non-adjacency relation.
\end{itemize}
\bibitem{Huchette:2017} Huchette, J., Vielma, J. P. (2017). A mixed-integer branching approach for very small formulations of disjunctive constraints. arXiv preprint arXiv:1709.10132.
\url{https://arxiv.org/abs/1709.10132}
\begin{itemize}
	\item  Small extended formulations for cyclic polytopes.
\end{itemize}
\bibitem{Davis-Stober:2017} Davis-Stober, C. P., Doignon, J. P., Fiorini, S., Glineur, F., Regenwetter, M. (2017). Extended Formulations for Order Polytopes through Network Flows. arXiv preprint arXiv:1710.02679.
\url{https://arxiv.org/abs/1710.02679}
\begin{itemize}
	\item Boolean quadric polytopes are faces of linear ordering polytopes. 
\end{itemize}
\bibitem{Seliverstov:2012} Селиверстов, А. В. (2012). Замечания о расположениях точек на квадриках. Модел. и анализ. информ. систем, 19(4), 72--77.
\url{http://www.mathnet.ru/links/1e4ce5781449a5d4b692e72999189785/mais248.pdf}
\begin{itemize}
	\item О числе фасет 2-смежностного многогранника.
\end{itemize}
\bibitem{Seliverstov:2013} Seliverstov, A. V. (2013). Monomials in quadratic forms. Journal of Applied and Industrial Mathematics, 7(3), 431--434. 
\url{https://link.springer.com/article/10.1134/S1990478913030162}
\begin{itemize}
	\item SAT Polytopes Are the Faces of the Polytopes of the Traveling Salesman Problem.
	\item An Analog of the Cook Theorem for Polytopes.
\end{itemize}
\bibitem{Seliverstov:2014} Селиверстов, А. В. (2014). Многогранники и связные подграфы. Дискретный анализ и исследование операций, 21(3), 82-86. \url{http://iitp.ru/upload/publications/6570/Seliverstov2014.pdf}
\begin{itemize}
	\item k-Смежностные грани булева квадратичного многогранника.
\end{itemize}
\bibitem{Simanchev:2014} Simanchev, R. Y. (2014). Combinatorial structure and adjacency of vertices of polytope of b-factors. Russian Mathematics, 58(6), 51--62. \url{https://link.springer.com/article/10.3103/S1066369X14060061}
\begin{itemize}
	\item On the Affine Reducibility of Combinatorial Polytopes.
\end{itemize}
\end{thebibliography}

\end{document}
Симанчев Р. Ю. Комбинаторная структура и смежность вершин политопа b-факторов //Известия высших учебных заведений. Математика. – 2014. – №. 6. https://cyberleninka.ru/article/n/kombinatornaya-struktura-i-smezhnost-vershin-politopa-b-faktorov

